Embedded Meta-Learning: Toward more flexible deep-learning models

### 2019-05-04 writing/embedded_meta_learning.tex
Conclusions, schematic fixes, tweaks

\begin{abstract}
How can deep learning systems flexibly reuse their knowledge? We suggest that the key is representing the task being performed along with the computations used to perform it. Specifically, we propose a new class of challenges, meta-mappings, which involve systematically transforming task behaviors. We draw inspiration from meta-learning and functional programming to propose a class of architectures that represent both data and tasks in a shared latent space. We demonstrate the flexibility of these architectures by showing that they can exhibit zero-shot remapping of behavior on new tasks. 
\end{abstract}

@@

In this paper, we propose a new class of tasks based on this idea: meta-mappings, i.e. mappings between tasks. For example, once a system has been trained to play a game, it should be able to alter its strategy in accordance with a change in task demands, such as trying to lose the game, or trying to play with an alteration in the reward function. The challenge is that the system must adapt to performing these tasks without seeing any data from the new task, only from either examples of similar transformations on different tasks (``here's how to change your go strategy to a losing one, here's how to change your checkers strategy to a losing one, now try to lose at chess'') or from natural language instructions (``try to lose at chess''). These mappings essentially provide a new opportunity for zero-shot transfer from one task to another -- that is, the system must transform its behavior to adapt to a new task without ever having seen training data from that task. This type of transfer is easily accessible to humans \citep{Lake2016}, but is generally inaccessible to most deep-learning models. \par
To address this challenge, we propose a new class of architectures which essentially take a functional perspective on meta-learning, and exploit the idea of homoiconicity\footnote{A homoiconic programming language is one in which programs in the language can be manipulated by programs in the language, just as data can.}. By treating task behaviors and data as functions, we can conceptually think of both data \emph{and} learned task behaviors as transformable. By embedding task behaviors, data, and language in the same space, we can conceptually think of both basic task solutions and adaptive functions, such as following instructions or altering behavior, as the same types of functional mappings. This yields the ability to not only learn to solve new tasks, but to learn how to flexibly transform these solutions in response to changing demands. We suggest that this ability will be key to building more intelligent and flexible deep learning systems. \par

@@

We propose a new class of Embedded Meta-Learning (EML) architectures which essentially separate the system into two parts: 

@@

Without training on these mappings, of course, the system will not be able to execute them well. However, if it is trained on a braod enough set of such mappings, it will be able to generalize these to new instances drawn from the same data/task distribution, as we demonstrate below. For instances that fall outside its data distribution or for optimal performance it may require some retraining. This reflects the structure of human behavior -- we are able to learn rapidly when new knowledge is relatively consistent with our previous knowledge, but learning an entirely new paradigm (such as calculus for a new student) can be quite slow. \par 

@@

\begin{tikzpicture}[auto]

@@

\node [conc] at (-6, -4) (perc) {\textbf{Input}};
%%\node [conc] at (-7.25, -2.5) (lang) {\textbf{Language}};
\node [conc] at (-6, 4) (act) {\textbf{Output}};
\node [block, text width=2cm] at (-4, -2) (IE) {$\bm{\mathcal{I}}$: \textbf{Input Encoder}};
%%\node [block, text width=2cm] at (-5, -0.5) (LE) {$\bm{\mathcal{L}}$: \textbf{Lang. Encoder}};
\node [block, text width=2.2cm] at (-3.5, 2.5) (OD) {$\bm{\mathcal{O}}$: \textbf{Output Decoder}};
\node [block, text width=2cm] at (-5.5, 1) (TE) {$\bm{\mathcal{T}}$: \textbf{Target Encoder}};
\path [line] (perc.north) to (IE.south);
%%\path [line] (lang.north) to ([xshift=0.05cm, yshift=0.05cm]LE.south west);
\path [line] ([xshift=-0.05cm, yshift=-0.05cm]IE.north east) to (rep.south west);
%%\path [line] (LE.east) to (rep.west);
\path [line] (rep.north west) to ([xshift=-0.05cm, yshift=0.05cm]OD.south east);
\path [line] (OD.north) to (act.south);
\path [line] (act.south) to (TE.north);
\path [line] (TE.east) to (rep.north west);

@@

\end{tikzpicture}
\caption{Schematic of our general architecure. Blocks with solid edges denote deep networks with learnable parameters, dashed edges represent inputs, outputs, embeddings, etc., and $f$ is a deep network with parameters specified by $\mathcal{H}$. Note that there may be multiple input, output, and target decoders if the system has multiple input modalities, e.g. both language and vision.} \label{architecture_fig}
\end{figure}
More formally, we take a \emph{functional} perspective on learning. A datum can be represented by a constant function which outputs it. (For example, each point in the latent space of an autoencoder can be thought of this way.) This allows us to interpret model inputs or outputs as functions. \par
We can then interpret most machine learning tasks as a mapping of functions to functions. These functions could represent data\footnote{Where ``data'' is a quite flexible term. The approach is relatively agnostic to whether the learning is supervised or reinforcement learning, whether inputs are images or natural language, etc.}, or they could be functions that operate on functions themselves. Under this perspective, learning tasks and learning to flexibly map between tasks, or learning to map from language to tasks, are all the same type of problem. \par
Specifically, we embed inputs, targets, and mappings into a shared representational space $Z$. Inputs are embedded by a deep network $\mathcal{I}: \text{input} \rightarrow Z$. Outputs are decoded from the representational space by a deep network $\mathcal{O}: Z \rightarrow \text{output}$. Targets are encoded by a deep network $\mathcal{T}: \text{targets} \rightarrow Z$. (Targets do not necessarily need to be output-like, e.g. in our RL tasks, we use (action, outcome) tuples as ``targets.'') \par
Given this, the task of mapping inputs to outputs can be framed as trying to find a transformation of the representational space that takes the (embedded) inputs from the training set to the (embedded) targets. These transformations are performed by a system with the following components:  
\begin{itemize}
\item $\mathcal{M}: \{(Z, Z), ...\} \rightarrow Z $ -- the meta network, which takes a set of (input embedding, target embedding) pairs and produces a function embedding. 
\item $\mathcal{H}: Z \rightarrow \text{parameters}$ -- the hyper network, which takes a function embedding and produces a set of parameters. 
\item $f: Z \rightarrow Z$ -- the transformation, implemented by a deep network with parameters specified by $\mathcal{H}$.
\end{itemize}
See Fig. \ref{architecture_fig} for a schematic of the architecture. \par

\subsection{Operation}
A basic forward pass through the system might look as follows.
\begin{enumerate}
\item A training dataset of (input, target) pairs is embedded by $\mathcal{I}$ and $\mathcal{T}$ to produce a set of paired embeddings. Another set of (possibly unlabeled) inputs is provided and embedded.
\item The meta network $\mathcal{M}$ maps the set of embedded (input, target) pairs to a function embedding.
\item The hyper network $\mathcal{H}$ maps the function embedding to parameters for $f$, which is used to transform the second set of inputs to a set of output embeddings.
\item The output embeddings are decoded by $\mathcal{O}$ to produce a set of outputs.
\end{enumerate}
To write this explicitly, suppose we have some dataset of input, target pairs ($D_1 = \{(x_0, y_0), ...\}$), and some input $x$ for which we wish to generate a predicted output $\hat{y}$. This output would be generated as follows: 
\[\hat{y} = \mathcal{O}\left(f_{D_1}\left(\mathcal{I} \left(x\right)\right) \right)\]
where $f_{D_1}$ is the transformation the meta-learner guesses for the training dataset $D_1$:
\[f_{D_1} \text{ is parameterized by } \mathcal{H}\left(\mathcal{M}\left( \left\{\left(\mathcal{I}\left(x_0\right), \mathcal{T}\left(y_0\right) \right), \left(\mathcal{I}\left(x_1\right), \mathcal{T}\left(y_1\right) \right), ... \right\}\right)\right)\]
This system can be trained end-to-end if labels are provided for a second set of inputs. In particular, suppose we have some loss function $\mathcal{L}(y, \hat{y})$ defined on a single target output $y$ and actual model output $\hat{y}$, for some input $x$. We define our total loss computed on some dataset $D_2$ as:
\[\mathbb{E}_{(x, y)\in {D}_2} \left[ \mathcal{L}\left(y, \mathcal{O}\left(f_{D_1}\left(\mathcal{I} \left(x\right)\right) \right)\right)\right]\]
More generally, suppose we have some input which is already embedded in the representation space $z_{in} \in Z$, and a task/function embedding $z_{\text{function}} \in Z$. Then we can generate an output $\hat{z}_{out} \in Z$ as:  
\[\hat{z}_{out} = f_{z_{\text{function}}}(z_{in}) \qquad \text{where } f_{z_{\text{function}}} \text{ is parameterized by } \mathcal{H}\left(z_{\text{function}}\right)\]
This output can then be appropriately dispatched depending on the task at hand. For example, if the $z_{in,i}$ are the system's embeddings for trying to win various games, and the $z_{out,i}$ are the corresponding embeddings for trying to lose those games, then $z_{out}$ could be interpreted as the system's guess at a losing strategy for the game embedded as $z_{in}$, and then could be used to play that game. We could then evaluate performance by how well the system actually performs at losing with the $z_{out}$ strategy. \par
Similarly, we could map from language to a task embedding, and then ask how well the system performs at the task specified by language. The key feature of our architecture -- the fact that tasks, data, and language are all embedded in a shared space -- allows substantial flexibility within a unified framework.

@@

\begin{figure}
\centering
\includegraphics[width=0.75\textwidth]{figures/poly/meta_results.png}
\caption{The system generalizes to apply learned meta-mappings to new tasks, and to apply unlearned meta-mappings from seeing examples. The solid line indicates optimal performance.} 
\label{poly_meta_map_results}
\end{figure}
As a proof of concept, we first evaluated the system on the simple task of learning polynomials in 4 variables of degree $\leq 2$ (i.e. the task was to learn functions of the form $f: \mathbb{R}^4 \rightarrow \mathbb{R}$ where $f \in \mathcal{P}_2 \left(\mathbb{R}\right)$). This yields an infinite family of base-level tasks (the vector space of all such polynomials), as well as many families of meta-mappings over tasks (for example, multiplying a polynomial by a constant, squaring a polynomial, or permuting its input variables). This allows us to not only examine the ability of the system to learn to learn polynomials from data, but also to adapt its learned representations in accordance with these meta-tasks. \par

@@

\subsection{Continual learning}
\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/continual/continual_learning.png}
\caption{Once the meta-learning system has been trained on a distribution of prior tasks, its performance on new tasks can be tuned by caching its guessed embeddings for the tasks and then optimizing those, thus avoiding any possibility of interfering with performance on prior tasks. Starting from random embeddings in the trained model results in slower convergence, while in an untrained model the embeddings cannot be optimized well.}
\label{poly_continual_results}
\end{figure}
Although the meta-learning approach is effective for rapidly adapting to a new task, it is unreasonable to think that our system must consider every example of a task it has seen at each inference step. We would like to be able to store our knowledge about the tasks in a way that allows it to be more carefully refined. Furthermore, we would like the system to be able to adapt to new tasks (that it cannot perfectly solve from examples) without catastrophically interfering with our prior knowledge \citep{McCloskey1989}. \par
A very simple solution to these problems is naturally suggested by our architecture. Specifically, task embeddings can be cached so that they don't have to be regenerated at each inference step. This also allows the potential to optimize these embeddings without altering the other parameters in the architecture, thus allowing fine-tuning on a task without seeing more examples, and without interfering with performance on any other task. That is, we can see the meta-learning step as a ``warm start'' for an optimization procedure over embeddings that are cached in memory \citep[c.f.][]{Kumaran2016}.\footnote{Note that the weights generated by the hyper network could be cached instead of the embeddings, which would be much more memory intensive but would allow even better tuning and would not require passing through the hyper network at inference time.} \par 
To test this idea, we pre-trained the system on 100 polynomial tasks, and then introduced 100 new tasks. We trained on these new tasks by starting from the meta-learning network's ``guess'' at the correct task embedding, and then optimizing this embedding without altering the other parameters. The results are shown in fig. \ref{poly_continual_results}. The meta-network embeddings offers good immediate performance, and substantially accelerates the optimization the process, compared to a randomly-initialized embedding. Furthermore, this ability to learn is due to training, not simply the expressiveness of the architecture, as is shown by attempting the same with an untrained network. \par

@@

\caption{Basic meta-learning successfully generalizes to held out tasks, both when trained on a random sample of half the tasks, or when a targeted subset is held out. The gray dashed line indicates chance performance, while the solid lines are optimal performance. The colored dashed lines show how well the system could perform by playing the strategy from the most correlated game it has seen. The fact that it generally exceeds this difficult baseline shows a deeper form of generalization than just memorizing a few strategies and picking the closest one.}

@@

\caption{The system can rapidly adapt to new tasks. (This figure shows training all parameters while replaying old tasks, unlike the continual learning strategy above.)}

@@

@@

Our work is an extrapolation from the rapidly-growing literature on meta-learning \citep[e.g.][]{Vinyals2016, Santoro2016, Finn2017a, Finn2018, Stadie2018}. It is also related to the literature on continual learning, or more generally tools for avoiding catastrophic interference based on architectural innovations \citep[e.g.][]{Fernando2017, Rusu2016}, regularization terms \citep[e.g.][]{Kirkpatrick2016, Zenke2017} or external memory \citep[e.g.][]{Sprechmann2018}. Recent work has also begun to blur the separation between these approaches, for example by meta-learning in an online setting \citep{Finn2019}. Our work is specifically inspired by the algorithms that attempt to have the system learn to adapt to a new task via activations rather than gradient descent \citep[e.g.][]{Wang2016a, Duan2016}. \par
Our architecture builds directly off of prior work on HyperNetworks \citep{Ha2016} -- networks which parameterize other networks -- and other recent applications thereof, such as guessing parameters for a model to accelerate model search \citep[e.g.][]{Brock2018a}. This is related to the longer history of work on different time-scales of weight adaptation \citep{Hinton1982} that has more recently been applied to meta-learning contexts \citep[e.g.][]{Ba2016, Munkhdalai2017}. It is more abstractly related to work on learning to propose architectures \citep[e.g.][]{Zoph2016}, and to models that learn to select and compose skills to apply to new tasks \citep[e.g.][]{Andreas, Andreas2016, Tessler2016, Reed2015}. In particular, some of the work in domains like visual question answering has explicitly explored the idea of building a classifier conditioned on a question \citep{Andreas, Andreasa}, which is related to one of the possible computational paths through our architecture. \par 
There has also been some recent interest in task (or function) embeddings. In simultaneous work Achille et al. \citep{Achille2019} proposed computing embeddings for tasks from the Fisher information of the parameters in a model tuned (final layer only) on the task. They show that this captures some interesting properties of the tasks, including some types of semantic relationships, and can help identify models that can perform well on a task. Other recent work has suggested a similar meta-learning framework where latent codes are computed for a task which can be decoded to a distribution over parameters \citep{Rusu2019}. Our perspective can be seen as a generalization of these that learns task embeddings in an end-to-end way, allows parameterizing a model (while some approaches only allow selection), but most importantly allows for remapping of behavior by meta-tasks. To the best of our knowledge none of the prior work has explored meta-mapping. \par

@@

* We've suggested that the separation of computations from knowledge of what is being computed in neural networks is limiting.

* We've suggested that the solution to this problem is the explicit representation of task alongside the computation.

* We've proposed a new type of generalization challenge?

* We see our proposal as a logical progression from the fundamental idea of meta-learning -- that there is a continuum between data and tasks. This naturally suggests the idea of manipulating task representations just like we manipulate data.

* We've proposed an architecture which represents data and tasks within the same latent space, and have demonstrated its flexibility.

* We've also shown that our approach provides a useful perspective on continual learning.

* We hope that these results will lead to the development of more powerful and flexible deep-learning models.

@@

\subsubsection{Card games}
\label{meth_data_cards}
Our card games were played with two suits, and 4 values per suit. In our setup, each hand in a game has a win probability (proportional to how it ranks against all other possible hands). The agent is dealt a hand, and then has to choose to bet 0, 1, or 2 (the three actions it has available). We considered a variety of games which depend on different features of the hand: 
\begin{itemize}
\item \textbf{High card:} Highest card wins.
\item \textbf{Pairs} Same as high card, except pairs are more valuable, and same suit pairs are even more valuable.
\item \textbf{Straight flush:} Most valuable is adjacent numbers in same suit, i.e. 4 and 3 in most valuable suit wins every time (royal flush).
\item \textbf{Match:} the hand with cards that differ least in value (suit counts as 0.5 pt difference) wins.
\item \textbf{Blackjack:} The hand's value increases with the sum of the cards until it crosses 5, at which point the player ``goes bust,'' and the value becomes negative. 
\end{itemize}
We also considered three binary options that could be altered to produce variants of these games:
\begin{itemize}
\item \textbf{Losers:} Try to lose instead of winning! Reverses the ranking of hands.
\item \textbf{Suits rule:} Instead of suits being less important than values, they are more important (essentially flipping the role of suit and value in most games).
\item \textbf{Switch suit:} Switches which of the suits is more valuable.
\end{itemize}
Any combination of these options can be applied to any of the 5 games, yielding 40 possible games. The systems were trained with the full 40 possible games, but after training we discovered that the ``suits rule'' option does not substantially alter the games we chose, so we have omitted it from our analyses.\par

>>>>

\begin{abstract}
How can deep learning systems flexibly reuse their knowledge? Toward this goal, we propose a new class of challenges, meta-mappings, which involve systematically transforming task behaviors. We suggest that the key to achieving this flexibility is representing the task being performed along with the computations used to perform it. We therfore draw inspiration from meta-learning and functional programming to propose a class of architectures that represent both data and tasks in a shared latent space. We demonstrate the flexibility of these architectures by showing that they can perform meta-mappings, i.e. that they can exhibit zero-shot remapping of behavior on new tasks. 
\end{abstract}

@@

In this paper, we propose a new class of tasks based on this idea: meta-mappings, i.e. mappings between tasks. For example, once a system has been trained to play a game, it should be able to alter its strategy in accordance with a change in task demands, such as trying to lose the game, or trying to play without using a certain action. The challenge is that the system must adapt to performing these tasks without seeing any data from the new task, only from either examples of similar transformations on different tasks (``here's how to change your go strategy to a losing one, here's how to change your checkers strategy to a losing one, now try to lose at chess'') or from natural language instructions (``try to lose at chess''). These mappings provide a new type of zero-shot transfer from one task to another -- the system must transform its behavior to adapt to a new task without ever having seen training data from that task. This type of transfer is easily accessible to humans \citep{Lake2016}, but is generally inaccessible to most deep-learning models. \par
To address this challenge, we propose a new class of architectures which essentially take a functional perspective on meta-learning, and exploit the idea of homoiconicity\footnote{A homoiconic programming language is one in which programs in the language can be manipulated by programs in the language, just as data can.}. By treating task behaviors and data as functions, we can conceptually think of both data \emph{and} learned task behaviors as transformable. By embedding task behaviors, data, and language in the same space, we can conceptually think of both basic task solutions and adaptive functions, such as following instructions or altering behavior, as mappings in function space. This yields the ability to not only learn to solve new tasks, but to learn how to flexibly transform these solutions in response to changing demands. We suggest that this ability will be key to building more intelligent and flexible deep learning systems. \par

@@

We propose a new class of Embedded Meta-Learning (EML) architectures which consist of two parts: 

@@

Without training on these mappings, of course, the system will not be able to execute them well. However, if it is trained on a braod enough set of such mappings, it will be able to generalize these to new instances drawn from the same data/task distribution, as we demonstrate below. For instances that fall outside its data distribution, or for optimal performance, it may require some retraining, however. This reflects the structure of human behavior -- we are able to learn rapidly when new knowledge is relatively consistent with our previous knowledge, but learning an entirely new paradigm (such as calculus for a new student) can be quite slow. \par 

@@

\begin{tikzpicture}[auto, scale=0.9]

@@

\node [conc] at (-7, -4) (perc) {\textbf{Input}};
%%\node [conc] at (-7.25, -2.5) (lang) {\textbf{Language}};
\node [conc] at (-7, 4) (act) {\textbf{Output}};
\node [block, text width=2cm] at (-4.5, -2) (IE) {$\bm{\mathcal{I}}$: \textbf{Input Encoder}};
%%\node [block, text width=2cm] at (-5, -0.5) (LE) {$\bm{\mathcal{L}}$: \textbf{Lang. Encoder}};
\node [block, text width=2.2cm] at (-4, 2.5) (OD) {$\bm{\mathcal{O}}$: \textbf{Output Decoder}};
\node [block, text width=2cm] at (-5.5, 1) (TE) {$\bm{\mathcal{T}}$: \textbf{Target Encoder}};
\path [line] (perc.north) to (IE.south);
%%\path [line] (lang.north) to ([xshift=0.05cm, yshift=0.05cm]LE.south west);
\path [line] ([xshift=-0.05cm, yshift=-0.05cm]IE.north east) to (rep.south west);
%%\path [line] (LE.east) to (rep.west);
\path [line] (rep.north west) to ([xshift=-0.05cm, yshift=0.05cm]OD.south east);
\path [line] (OD.north) to (act.south);
\path [line] (act.south) to (TE.north);
\path [line] (TE.east) to (rep.north west);

@@

\end{tikzpicture}
\caption{Schematic of our general architecure. Blocks with solid edges denote deep networks with learnable parameters, dashed edges represent inputs, outputs, embeddings, etc., and $f$ is a deep network with parameters specified by $\mathcal{H}$. Note that there may be multiple input, output, and target decoders if the system has multiple input modalities, e.g. both language and vision.} \label{architecture_fig}
\end{figure}
More formally, we take a \emph{functional} perspective on learning. A datum can be represented by a constant function which outputs it. (For example, each point in the latent space of an autoencoder can be thought of this way.) This allows us to interpret model inputs or outputs as functions. We can then interpret most machine learning tasks as a mapping of functions to functions. These functions could represent data\footnote{Where ``data'' is a quite flexible term. The approach is relatively agnostic to whether the learning is supervised or reinforcement learning, whether inputs are images or natural language, etc.}, or they could be functions that operate on functions themselves. Under this perspective, learning tasks and learning to flexibly map between tasks, or learning to map from language to tasks, are all the same type of problem. \par
Specifically, we embed inputs, targets, and mappings into a shared representational space $Z$. Inputs are embedded by a deep network $\mathcal{I}: \text{input} \rightarrow Z$. Outputs are decoded from the representational space by a deep network $\mathcal{O}: Z \rightarrow \text{output}$. Targets are encoded by a deep network $\mathcal{T}: \text{targets} \rightarrow Z$. (Targets do not necessarily need to be output-like, e.g. in our RL tasks, we use (action, outcome) tuples as ``targets.'') \par
Given this, the task of mapping inputs to outputs can be framed as trying to find a transformation of the representational space that takes the (embedded) inputs from the training set to the (embedded) targets. These transformations are performed by a system with the following components:  
\begin{itemize}
\item $\mathcal{M}: \{(Z, Z), ...\} \rightarrow Z $ -- the meta network, which takes a set of (input embedding, target embedding) pairs and produces a function embedding. 
\item $\mathcal{H}: Z \rightarrow \text{parameters}$ -- the hyper network, which takes a function embedding and produces a set of parameters. 
\item $f: Z \rightarrow Z$ -- the transformation, implemented by a deep network with parameters specified by $\mathcal{H}$.
\end{itemize}
See Fig. \ref{architecture_fig} for a schematic of the architecture. \par

\subsection{Operation}
A basic forward pass through the system might look as follows.
\begin{enumerate}
\item A training dataset of (input, target) pairs is embedded by $\mathcal{I}$ and $\mathcal{T}$ to produce a set of paired embeddings. Another set of (possibly unlabeled) inputs is provided and embedded.
\item The meta network $\mathcal{M}$ maps the set of embedded (input, target) pairs to a function embedding.
\item The hyper network $\mathcal{H}$ maps the function embedding to parameters for $f$, which is used to transform the second set of inputs to a set of output embeddings.
\item The output embeddings are decoded by $\mathcal{O}$ to produce a set of outputs.
\end{enumerate}
To write this explicitly, suppose we have some dataset of input, target pairs ($D_1 = \{(x_0, y_0), ...\}$), and some input $x$ for which we wish to generate a predicted output $\hat{y}$. This output would be generated as follows: 
\[\hat{y} = \mathcal{O}\left(f_{D_1}\left(\mathcal{I} \left(x\right)\right) \right)\]
where $f_{D_1}$ is the transformation the meta-learner guesses for the training dataset $D_1$:
\[f_{D_1} \text{ is parameterized by } \mathcal{H}\left(\mathcal{M}\left( \left\{\left(\mathcal{I}\left(x_0\right), \mathcal{T}\left(y_0\right) \right), \left(\mathcal{I}\left(x_1\right), \mathcal{T}\left(y_1\right) \right), ... \right\}\right)\right)\]
This system can be trained end-to-end if labels are provided for the second set of inputs. In particular, suppose we have some loss function $\mathcal{L}(y, \hat{y})$ defined on a single target output $y$ and actual model output $\hat{y}$, for some input $x$. We define our total loss computed on some dataset $D_2$ as:
\[\mathbb{E}_{(x, y)\in {D}_2} \left[ \mathcal{L}\left(y, \mathcal{O}\left(f_{D_1}\left(\mathcal{I} \left(x\right)\right) \right)\right)\right]\]
More generally, suppose we have some input which is already embedded in the representation space $z_{in} \in Z$, and a task/function embedding $z_{\text{function}} \in Z$. Then we can generate an output $\hat{z}_{out} \in Z$ as:  
\[\hat{z}_{out} = f_{z_{\text{function}}}(z_{in}) \qquad \text{where } f_{z_{\text{function}}} \text{ is parameterized by } \mathcal{H}\left(z_{\text{function}}\right)\]
This output can then be appropriately dispatched depending on the task at hand. For example, if the $z_{in,i}$ are the system's embeddings for trying to win various games, and the $z_{out,i}$ are the corresponding embeddings for trying to lose those games, then $z_{out}$ could be interpreted as the system's guess at a losing strategy for the game embedded as $z_{in}$, and then could be used to play that game. We could then evaluate performance by how well the system actually performs at losing with the $z_{out}$ strategy. \par
Similarly, we could map from language to a task embedding, and then ask how well the system performs at the task specified by language. The key feature of our architecture -- the fact that tasks, data, and language are all embedded in a shared space -- allows substantial flexibility within a unified framework.

@@

\begin{figure}
\centering
\includegraphics[width=0.75\textwidth]{figures/poly/meta_results.png}
\caption{The system generalizes to apply learned meta-mappings to new tasks, and to apply unlearned meta-mappings from seeing examples. The solid line indicates optimal performance.} 
\label{poly_meta_map_results}
\end{figure}
As a proof of concept, we first evaluated the system on the simple task of learning polynomials of degree $\leq 2$ in 4 variables (i.e. the task was to regress functions of the form $f: \mathbb{R}^4 \rightarrow \mathbb{R}$ where $f \in \mathcal{P}_2 \left(\mathbb{R}\right)$). This yields an infinite family of base-level tasks (the vector space of all such polynomials), as well as many families of meta-mappings over tasks (for example, multiplying a polynomial by a constant, squaring a polynomial, or permuting its input variables). This allows us to not only examine the ability of the system to learn to learn polynomials from data, but also to adapt its learned representations in accordance with these meta-tasks. \par

@@

\subsection{Continual learning}
\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/continual/continual_learning.png}
\caption{Once the meta-learning system has been trained on a distribution of prior tasks, its performance on new tasks can be tuned by caching its guessed embeddings for the tasks and then optimizing those, thus avoiding any possibility of interfering with performance on prior tasks. Starting from random embeddings in the trained model results in slower convergence, while in an untrained model the embeddings cannot be optimized well.}
\label{poly_continual_results}
\end{figure}
Although the meta-learning approach is effective for rapidly adapting to a new task, it is unreasonable to think that our system must consider every example of a task it has seen at each inference step. We would like to be able to store our knowledge about the tasks in a way that allows it to be more carefully refined. Furthermore, we would like the system to be able to adapt to new tasks (that it cannot perfectly solve from examples) without catastrophically interfering with our prior knowledge \citep{McCloskey1989}. \par
A very simple solution to these problems is naturally suggested by our architecture. Specifically, task embeddings can be cached so that they don't have to be regenerated at each inference step. This also allows optimization of these embeddings without altering the other parameters in the architecture, thus allowing fine-tuning on a task without seeing more examples, and without interfering with performance on any other task. That is, we can see the meta-learning step as a ``warm start'' for an optimization procedure over embeddings that are cached in memory \citep[c.f.][]{Kumaran2016}.\footnote{Note that the weights generated by the hyper network could be cached instead of the embeddings, which would be much more memory intensive but would allow even better tuning and would not require passing through the hyper network at inference time.} \par 
To test this idea, we pre-trained the system on 100 polynomial tasks, and then introduced 100 new tasks. We trained on these new tasks by starting from the meta-learning network's ``guess'' at the correct task embedding, and then optimizing this embedding without altering the other parameters. The results are shown in fig. \ref{poly_continual_results}. The meta-network embeddings offers good immediate performance, and substantially accelerates the optimization the process, compared to a randomly-initialized embedding (see supp. fig. \ref{supp_poly_continual_results} for a more direct comparison). Furthermore, this ability to learn is due to training, not simply the expressiveness of the architecture, as is shown by attempting the same with an untrained network. \par

@@

\caption{Generalization to held-out tasks.}

@@

\caption{Rapid integration once held-out tasks are introduced.}

@@

\caption{Basic meta learning in the cards domain. (a) The system successfully generalizes to held out tasks, both when trained on a random sample of half the tasks, or when a targeted subset is held out. The gray dashed line indicates chance performance, while the solid lines are optimal performance. The colored dashed lines show how well the system could perform by playing the strategy from the most correlated game it has seen. The fact that it generally exceeds this difficult baseline shows a deeper form of generalization than just memorizing a few strategies and picking the closest one. (b) The system can rapidly adapt to new tasks. (This figure shows the effect of training all parameters while replaying old tasks, unlike the continual learning strategy above.)}

@@

Our work is an extrapolation from the rapidly-growing literature on meta-learning \citep[e.g.][]{Vinyals2016, Santoro2016, Finn2017a, Finn2018, Stadie2018}. It is also related to the literature on continual learning, or more generally tools for avoiding catastrophic interference based on architectural innovations \citep[e.g.][]{Fernando2017, Rusu2016}, regularization terms \citep[e.g.][]{Kirkpatrick2016, Zenke2017} or external memory \citep[e.g.][]{Sprechmann2018}. Recent work has also begun to blur the separation between these approaches, for example by meta-learning in an online setting \citep{Finn2019}. Our work is specifically inspired by the algorithms that attempt to have the system learn to adapt to a new task via activations rather than weight updates \citep[e.g.][]{Wang2016a, Duan2016}. \par
Our architecture builds directly off of prior work on HyperNetworks \citep{Ha2016} -- networks which parameterize other networks -- and other recent applications thereof, such as guessing parameters for a model to accelerate model search \citep{Brock2018a}. This is related to the longer history of work on different time-scales of weight adaptation \citep{Hinton1982, Kumaran2016} that has more recently been applied to meta-learning contexts \citep[e.g.][]{Ba2016, Munkhdalai2017}. It is more abstractly related to work on learning to propose architectures \citep[e.g.][]{Zoph2016}, and to models that learn to select and compose skills to apply to new tasks \citep[e.g.][]{Andreas, Andreas2016, Tessler2016, Reed2015}. In particular, some of the work in domains like visual question answering has explicitly explored the idea of building a classifier conditioned on a question \citep{Andreas, Andreasa}, which is related to one of the possible computational paths through our architecture. \par 
There has also been some recent interest in task (or function) embeddings. In simultaneous work Achille et al. \citep{Achille2019} proposed computing embeddings for tasks from the Fisher information of the parameters in a model tuned (final layer only) on the task. They show that this captures some interesting properties of the tasks, including some types of semantic relationships, and can help identify models that can perform well on a task. Other recent work has suggested a similar meta-learning framework where latent codes are computed for a task which can be decoded to a distribution over parameters \citep{Rusu2019}. Our perspective can be seen as a generalization of these that learns task embeddings in an end-to-end way, allows parameterizing a model (while some approaches only allow selection), but most importantly allows for remapping of behavior by meta-tasks. To the best of our knowledge none of the prior work has explored meta-mappings. \par

@@

In this paper, we've highlighted a new type of flexibility in the form of \emph{meta-mappings}, that is, mappings between tasks. We've suggested that achieving this type of flexibility is difficult in most deep learning architectures, because they separate computation from the knowledge of what is being computed. We've proposed that representing the task explicitly as the computation provides a solution to this problem. To this end, we've proposed a meta-learning system which embeds tasks and data into a shared latent space, and then meta-learns to make mappings over this space. We see our proposal as a logical progression from the fundamental idea of meta-learning -- that there is a continuum between data and tasks. This naturally suggests the idea of manipulating task representations just like we manipulate data. We've shown that this approach yields considerable flexibility, most importantly the ability to adapt zero-shot to a new task from examples of task transformations. We've also shown that our approach provides a useful perspective on continual learning. We hope that these results will lead to the development of more powerful and flexible deep-learning models. \par
%\subsubsection*{Acknowledgements}
%We would like to acknowledge Noah Goodman, Surya Ganguli, Katherine Hermann, Erin Bennett, and Arianna Yuan for stimulating questions and suggestions on this project.

@@

\subsubsection{Card games}
\label{meth_data_cards}
Our card games were played with two suits, and 4 values per suit. In our setup, each hand in a game has a win probability (proportional to how it ranks against all other possible hands). The agent is dealt a hand, and then has to choose to bet 0, 1, or 2 (the three actions it has available). We considered a variety of games which depend on different features of the hand: 
\begin{itemize}
\item \textbf{High card:} Highest card wins.
\item \textbf{Pairs} Same as high card, except pairs are more valuable, and same suit pairs are even more valuable.
\item \textbf{Straight flush:} Most valuable is adjacent numbers in same suit, i.e. 4 and 3 in most valuable suit wins every time (royal flush).
\item \textbf{Match:} the hand with cards that differ least in value (suit counts as 0.5 pt difference) wins.
\item \textbf{Blackjack:} The hand's value increases with the sum of the cards until it crosses 5, at which point the player ``goes bust,'' and the value becomes negative. 
\end{itemize}
We also considered three binary options that could be altered to produce variants of these games:
\begin{itemize}
\item \textbf{Losers:} Try to lose instead of winning! Reverses the ranking of hands.
\item \textbf{Suits rule:} Instead of suits being less important than values, they are more important (essentially flipping the role of suit and value in most games).
\item \textbf{Switch suit:} Switches which of the suits is more valuable.
\end{itemize}
Any combination of these options can be applied to any of the 5 games, yielding 40 possible games. The systems were trained with the full 40 possible games, but after training we discovered that the ``suits rule'' option does not substantially alter the games we chose (in the sense that the probability of a hand winning in the two variants of a game is very highly correlated), so we have omitted it from our analyses.\par
